Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-25 paper/paper.tex
Wrote something in every section of methods

Unfortunately, potential scientific advances are hindered [by image quality] as well as [more so?] the lack of high-quality and pertinent metadata associated with the image collections. Many specimen collections include Darwin Core metadata, detailing specimen taxon, geographic location, and several other descriptive aspects. Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a human examining several images at a time, they are insufficient for researchers seeking to apply computational methods to examine thousands of images to determine if, for instance, a dorsal fin of a specific fish has a different shape. Since the collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible. Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.

@@

\section{Methods}

\subsection{Detectron}
\subsection{Pixel Analysis}
The masks and bounding boxes produced by \verb|detectron| are generally quite good, although they are almost never perfect. They almost always either include additional background as part of the fish, or clip part(s) of the fish outside the bounding box. To solve this shortcoming, we utilize pixel analysis methods commonly found in image informatics.

>>>>

Unfortunately, potential scientific advances are hindered [by image quality] as well as [more so?] the lack of high-quality and pertinent metadata associated with the image collections. Many specimen collections include Darwin Core metadata, detailing specimen taxon, geographic location, and several other descriptive aspects. Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a human examining several images at a time, they are insufficient for researchers seeking to apply computational methods to examine thousands of images to determine if, for instance, a dorsal fin of a specific fish has a different shape. Since the collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible. Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.~\cite{Leipzig2021.01.28.428644}\todo{Throwing in Jeremy's paper somewhere}

@@

\section{Methods}
Our process for metadata generation can be broken into 3 steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image informatics analysis at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.

\subsection{Detectron}
A prerequisite task to addressing any more advanced metadata property determination is finding specimens (and other relevant objects) within collection images. Object detection has been an incredibly active field of study in recent years,~\cite{zou2019object} and has resulted in a number of well tested purpose built architectures. We elected to use Facebook AI Research's \verb|detectron| tool~\cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture~\cite{he2018mask}, for object detection in our project.

\verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format dataset. It is able to handle an arbitrary number of object classes, and can classify an arbitrary number of object within a given sample. For our project, we are currently using it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers.
\subsection{Pixel Analysis}
The masks and bounding boxes produced by \verb|detectron| are generally quite good, although they are almost never perfect. They almost always either include additional background as part of the fish, or clip part(s) of the fish outside the bounding box. To solve this shortcoming, we utilize pixel analysis methods commonly found in image informatics.
